Blum axioms and nondeterministic computation of functions

### 2015-12-15 paper.tex
paper.tex: Add intended paper structure.
paper.tex: Improve title precision.
paper.tex: \usepackage[T1]{fontenc}.
paper.tex: Add introductory text about Gödel numberings.

\usepackage[utf8]{inputenc}

@@

\title{Blum axioms and nondeterministic computation}

@@

>>>>

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}

\usepackage{complexity}

@@

\title{Blum axioms and nondeterministic computation of functions}

@@

\section{Introduction}

\section{Gödel numberings}

% TODO: Note that this is a simplification

Gödel's famous Incompleteness Theorem says that
any correct and consistent formal system that includes the Peano arithmetic
will have statements that are true under that system,
but \emph{cannot be proven} under that system.
In essence,
in the proof of this theorem,
Gödel created self-referential proposition $\varphi$
that essentially says ``$\varphi$ is not provable''.
Then, if $\varphi$ is false,
by it's own assertion, it must be provable;
but, as the system is consistent,
this would mean that $\varphi$ is true
--- a contradiction.
Hence, $\varphi$ must be true.
But, as it is true,
there cannot be a proof under the current formal system to it
--- that is exactly what $\varphi$ asserts.
So,
we get a proposition we know it is true,
but we cannot prove it using only tools of that system.

We can have a glimpse at how Gödel managed to construct a formula like $\varphi$
by analyzing how Turing constructed a language
that cannot be decided by Turing machines.

The language built by Turing is known today as the halting problem.
In essence,
you are given a Turing machine $M$ and an input $w$
and must decide whether $M$ eventually halts when processing $w$.
To prove that this problem is undecidable,
Turing had first to somehow encode this problem as a language
(because all a Turing machine can understand are sentences of a language);
the key point is that the Turing machine formalism
had to be encoded into words that could be fed to Turing machines.
Thus we could pick any machine and feed its own description as an input;
this form of self-reference is analogous
to Gödel's unprovable but true sentence.

In our context,
a \emph{Gödel numbering} will simply be a means
of associating every word $w$ of $\{0, 1\}^*$
with a computable function.
Section~\ref{sec:acceptable-godel-numberings} shows a refinement of this notion,
and section~\ref{sec:blum-axioms}
defines the Blum axioms over the refined definition.

\subsection{Acceptable Gödel numberings}
\label{sec:acceptable-godel-numberings}

\subsection{Blum axioms}
\label{sec:blum-axioms}

\section{Nondeterministic computation of functions}

\subsection{Hopcroft-Ullman definition}
\subsection{Oded Goldreich definition}
\subsection{Krentel's $\OptP$ class}
\subsection{Valiant's $\#\P$ class}
\subsection{Alternative approaches for nondeterministic functions}
